### 2016-09-14 doc/manuscript.Rmd
Added CONSORT fig in manuscript + image file
Added results to the TAGFA manuscript

@@

- Primary analysis:
    - Heatmap
    - GEE
        - Include # of both uncorrected and corrected (FDR) significant associations
        - QIC modeling
        - DAG development
        - Look over the entire model (see which variables are significant, etc)
        - Sensitivity analysis with Carb intake? And with adiponectin? (which is
        involved in TAG metabolism)
    - PLS with ISI and HOMA-IR
        - CV for determining number of comps (best is 2)
        - Loadings (of TAGFA) (tho all are the same, use HOMA/ISI. BCF have
        lower corr between measured and predicted) (Use COrr of both components
        (1 and 2))
        - Prediction (of predicted vs real) (in the pls.rmd file, not in
        manuscript (or maybe in ESM?))
        - Use extracted PLS components in GEE (?)
        - Train and test (CV) to see how it predicts in a new dataset (ie. a
        future visit) (done. In pls.rmd file. As ESM?)
- Secondary analysis:
    - PLS-DA (dysgly)
        - Train and test (CV)
        - Loadings (of TAGFA) 
        - Groupings
        - Prediction (misclassification)
    - AROC
        - dysgly with clinical TAG vs the 'best' fatty acid to compare to

@@

```{r analyze_gee, cache=TRUE}
gee_df <- analyze_gee()
```

@@

tagfa <- calc_tagfa_percent()
outcome_chg <- calc_outcome_changes()
female <- calc_discr_npct(ds0yr$Sex, 'Female')
euro <- calc_discr_npct(ds0yr$Ethnicity, 'European')
estci <- calc_gee_estci(gee_df)
fa_cor <- calc_cor()
cor_pls_homa <- calc_pred_corr(pls_homa_t, pls_homa_t$test_data)
cor_pls_isi <- calc_pred_corr(pls_isi_t, pls_isi_t$test_data)
```

@@

Basic characteristics/demographics

`r tab_basic` shows some basic character

The outcome variables significantly decreased over the 6 years by a median 
`r outcome_chg$chg` (p`r outcome_chg$p`; n=`r outcome_chg$n`).

`r fig_tagfa` shows the distribution of each TAGFA (see `r stab_tagfa` for mean
and SD {{ confirm }}). Three TAGFA contributed 
`r format_rounding(sum(tagfa$pct))`% to the total TAG concentration:
`r tagfa$c[1]`; `r tagfa$c[2]`; and, `r tagfa$c[3]`.

`r fig_corr` shows a heatmap of the correlation of individual TAGFA with the
outcome variables and several basic characteristics.
As expected, nearly all TAGFA had very strong positive correlations (r=
`r fa_cor$rng$TAG`) with clinically-measured TAG. There was also moderate
negative correlations with HDL (r=`r fa_cor$rng$HDL`). For the outcome variables,
the correlations for the insulin sensitivity measures were generally higher 
(1/HOMA-IR: r=`r fa_cor$rng['1/HOMA-IR']`, ISI: r=`r fa_cor$rng$ISI`) than 
for the beta-cell function measures (all r<0.30).

@@

Main effect

There were {{ ## }} significant associations in the unadjusted GEE model shown
in {{ `r sfig_gee` }}. Only a few associations were attenuated after full model
adjustment primarily with the beta-cell function outcomes, as shown in 
`r fig_gee`. As a concentration, nearly all TAGFA had a strong negative
association on 1/HOMA-IR and ISI, and a few had strong negative associations
with IGI/IR and ISSI-2. As a mol%, four TAGFA (14:0, 16:0, 14:1n-7, and 16:1n-7)
had negative associations with 1/HOMA-IR and ISI (between {{ ## }}% lower
insulin sensitivity for every SD increase in the TAGFA), while several more TAGFA had
positive associations with 1/HOMA-IR and ISI (20:0, 18:1n-9, 20:1n-9, 22:1n-9,
18:2n-6, 20:2n-6, 20:4n-6, and 22:5n-3) predicting a {{ ## }}% higher insulin
sensitivity for every SD increase in the TAGFA. 
One TAGFA, 20:2n-6, had a very strong positive association with the
insulin sensitivity measures, with a {{ ## }}% higher insulin sensitivity for
every SD increase in 20:2n-6.

Both clinically-measured TAG and total TAGFA concentration had very strong
negative associations with all outcome variables.

There were no significant interactions by time, sex, or ethnicity for any of the
TAGFA (data not shown).

@@

Accuracy of predictive ability of PLS components with real measure {{use test maybe?}}.
Correlation of pred vs real in test set.

The predictive ability of the PLS analysis using the TAGFA composition

`r fig_pls`

The correlation between the predicted values of the outcome variables from the
PLS analysis compared to the actual value was `r cor_pls_homa$r` 
(p`r cor_pls_homa$p`) for 1/HOMA-IR and `r cor_pls_isi$r` (p`r cor_pls_isi$p`) 
for ISI, suggested TAGFA composition has moderate predictive ability for 
insulin sensitivity measures.

`r calc_pred_corr()`

@@

@@

```{r fig_gee}
plot_gee_main(gee_df)
```

```{r table_gee_main}
table_gee_main(gee_df)
```

>>>>

- Run PLS with just those FA that loaded strongly to see the predictive ability.

@@

- Primary analysis:
    - Look over medications, how they influence the TAGFA
    - Heatmap
    - GEE
        - SA for the large outlier for the TAGFA (see dist plot)
        - Include # of both uncorrected and corrected (FDR) significant associations
        - QIC modeling
        - DAG development
        - Look over the entire model (see which variables are significant, etc)
        - Sensitivity analysis with Carb intake? And with adiponectin? (which is
        involved in TAG metabolism)
    - PLS with ISI and HOMA-IR
        - CV for determining number of comps (best is 2)
        - Loadings (of TAGFA) (tho all are the same, use HOMA/ISI. BCF have
        lower corr between measured and predicted) (Use COrr of both components
        (1 and 2))
        - Prediction (of predicted vs real) (in the pls.rmd file, not in
        manuscript (or maybe in ESM?))
        - Use extracted PLS components in GEE (?)
        - Train and test (CV) to see how it predicts in a new dataset (ie. a
        future visit) (done. In pls.rmd file. As ESM?)
- Secondary analysis:
    - PLS-DA (dysgly)
        - Train and test (CV)
        - Loadings (of TAGFA) 
        - Groupings
        - Prediction (misclassification)
    - AROC
        - dysgly with clinical TAG vs the 'best' fatty acid to compare to

- Make sure to include comments from NEFA paper
- Add stats to basic char table... (don't really want to. But I should ..?)

@@

```{r analyze_gee, cache=TRUE}
gee_adj_df <- analyze_gee()
gee_unadj_df <- analyze_gee(covars = "VN")
```

@@

tagfa <- calc_tagfa_percent()
outcome_chg <- calc_outcome_changes()
female <- calc_discr_npct(ds0yr$Sex, 'Female')
euro <- calc_discr_npct(ds0yr$Ethnicity, 'European')
fhd <- calc_discr_npct(ds0yr$FamHistDiab, 'Yes')
est0 <- calc_gee_estci(gee_unadj_df)
est1 <- calc_gee_estci(gee_adj_df)
fa_cor <- calc_cor()
cor_pls_homa <- calc_pred_corr(pls_homa_t, pls_homa_t$test_data)
cor_pls_isi <- calc_pred_corr(pls_isi_t, pls_isi_t$test_data)
```

@@

`r tab_basic` shows some basic characteristics of the PROMISE cohort. There were
`r female$npct` females and `r euro$npct` who had European-ancestry, with a mean
age in years of `r aide::ave_sd(ds0yr$Age)` and a mean BMI
of `r aide::ave_sd(ds0yr$BMI)`. Given the eligibility criteria, the majority of
participants (`r fhd$npct`) had a family history of diabetes.
Between the baseline visit and the 6-year visit in this sample, insulin
sensitivity and beta-cell function measures had a significant median decline
between `r outcome_chg$chg` (p`r outcome_chg$p`; n=`r outcome_chg$n`). There 
were `r dys$dm` and `r dys$pre` incident cases of diabetes and
pre-diabetes (IFG and IGT), respectively. {{ confirm this is incidence }}

`r fig_tagfa` shows the composition of each FA in the TAG fraction (see 
`r stab_tagfa` for raw numerical values of the mean and SD {{ confirm }}). 
Three TAGFA contributed `r format_rounding(sum(tagfa$pct))`% to the total 
TAG concentration: `r tagfa$c[1]`; `r tagfa$c[2]`; and, `r tagfa$c[3]`.
`r fig_corr` shows a heatmap of the correlation of individual TAGFA with the
outcome variables and several basic characteristics.
As expected, nearly all TAGFA had very strong positive correlations (r=
`r fa_cor$rng$TAG`) with clinically-measured TAG and moderate positive 
correlations with WC (r=`r fa_cor$rng$Waist`). There was also moderate
negative correlations with HDL (r=`r fa_cor$rng$HDL`). For the outcome variables,
the correlations for the insulin sensitivity measures were generally higher 
(1/HOMA-IR: r=`r fa_cor$rng['1/HOMA-IR']`, ISI: r=`r fa_cor$rng$ISI`) than 
for the beta-cell function measures (all r<0.30).

@@

There were `r nrow(dplyr::filter(gee_unadj_df, p.value <= 0.05))` FDR-corrected 
significant associations in the unadjusted GEE model (see {{ `r fig_gee_unadj` 
}}) and `r nrow(dplyr::filter(gee_adj_df, p.value <= 0.05))` FDR-corrected
significant associations in the adjusted GEE model as shown in `r fig_gee_adj`. 
The majority of associations with beta-cell function measures were attenuated
after full model adjustment, while nearly all associations with insulin
sensitivity remained significant. {{ confirm }} Subsequent analysis revealed
that the attenuation with beta-cell function was due primarily to adjustment for
{{ waist? ALT? }}.

As a concentration, nearly all TAGFA had a strong negative association on
1/HOMA-IR {{ change to HOMA2-IS }} and ISI (estimates ranging from 
`r est1$outcome_b$rng[3]` and `r est1$outcome_b$rng[7]`, respectively), and a
few had strong negative associations with IGI/IR and ISSI-2 (estimates ranging 
from `r est1$outcome_b$rng[10]` and `r est1$outcome_b$rng[13]`, respectively).
As a mol%, four TAGFA (14:0, 16:0, 14:1n-7, and 16:1n-7) had negative
associations with 1/HOMA-IR and ISI (between `r est1$outcome_b$rng[1]` and 
`r est1$outcome_b$rng[5]`%, respectively, lower insulin sensitivity for every SD
increase in the TAGFA), while several more TAGFA had positive associations with
1/HOMA-IR and ISI (20:0, 18:1n-9, 20:1n-9, 22:1n-9, 18:2n-6, 20:2n-6, 20:4n-6,
and 22:5n-3) predicting between `r est1$outcome_b$rng[2]` and 
`r est1$outcome_b$rng[6]`%, respectively, higher insulin sensitivity for every
SD increase in the TAGFA. One TAGFA, 20:2n-6, had a very strong positive
association with the insulin sensitivity measures, with a `r est1$b_ci$est[1]`
to `r est1$b_ci$est[36]`% higher insulin sensitivity for every SD increase in 
20:2n-6.

Both clinically-measured TAG and total TAGFA concentration had very strong
negative associations with all outcome variables. There were no significant
interactions by time, sex, or ethnicity for any of the TAGFA (data not shown).

@@

Clustering analysis using PLS, shown in `r fig_pls`, revealed that 14:0, 14:1n-7,
16:0, and 16:1n-7 loaded strongly (meaning the FA fell between the dashed and
solid circles) and negatively on 1/HOMA-IR and ISI, suggesting this cluster of
TAGFA tracks together with lower insulin sensitivity. The TAGFA 20:2n-6,
20:5n-3, 22:5n-3, and 22:6n-3 loaded positively on both insulin sensitivity 
measures. No other TAGFA loaded strongly, and the results of which remained
after running the PLS model on the testing set. The predictive ability of the 
PLS model, determined by correlating the predicted outcome values with the actual 
values, were good (1/HOMA-IR: `r cor_pls_homa$r_p`; ISI: `r cor_pls_isi$r_p`).

@@

![`r fig_consort`](../img/flowDiagramSample.png)

@@

```{r fig_gee}
plot_gee_main(gee_unadj_df)
plot_gee_main(gee_adj_df)
```

```{r table_gee_main}
table_gee_main(gee_unadj_df)
table_gee_main(gee_adj_df)
```
